Paper 2 !DRAFT! Do not circulate!

### 2014-08-04 Articles/Article_EcolEcon_2014/Paper2.Rnw
Now including a historical graph.

<<setup, echo=FALSE, message=FALSE, eval=TRUE>>=
require(EconModels)
require(EconData)
# require(lattice)
# require(latticeExtra)
require(ggplot2)
# require(car)
# require(mosaic)
# require(xtable)
# require(nlmrt)
# require(micEconCES)
require(plyr)
# require(dplyr)
# Provides access to data melting. 
# See http://cran.r-project.org/web/packages/reshape2/reshape2.pdf
# require(reshape2) 
# tikz allows use of LaTeX formatting and font in graphs. 
# Allows for a consistent look across the paper.
# See http://r-forge.r-project.org/R/?group_id=440 for instructions 
# on installing tikzDevice.
# require(tikzDevice) 
# trellis.par.set(theme=theme.mosaic())
# options(width=75)
# options(show.signif.stars=TRUE)
require(knitr)

@@

Graph(s) of historical data here.

>>>>

<<setup, echo=FALSE, message=FALSE, eval=TRUE>>=
require(EconModels)
require(EconData)
require(ggplot2)
require(plyr)
# Provides access to data melting. 
# See http://cran.r-project.org/web/packages/reshape2/reshape2.pdf
require(reshape2) 
require(knitr)

@@

Figure~\ref{fig:Historical_Data} shows a graph of historical data.

<<Historical_Data, fig.pos="H", fig.align='center', fig.width=6.6, fig.height=3, fig.cap="Historical data.">>=
historicalPlot(historicalData, 
               facet_formula = Country ~ Source, 
               lines_formula = iGDP + iK + iL + iXp + iXf + iU ~ Year, 
               line_types = c(1,2,3,4,5,6)) + 
  xlab("") + 
  ylab("Indexed (1960=1)")
@
